chronologies

### 2017-12-20 analysis/chronos/analysis_chronologies.Rmd
update chronos

@@

```{r chronos_4_sites_collapsed}
plot_cro_sites_collapsed <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  # geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)
```

>>>>

plot_cro_sites
```

@@

```{r chronos_4_sites_collapsed}
plot_cro_sites_collapsed <- cro_sites %>% ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  # geom_point(size=1) +
  theme(panel.grid = element_blank(),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  scale_fill_manual(values = c('#1b9e77','#d95f02','#7570b3','#e7298a')) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10)) 
#  geom_smooth(method= 'loess', span = 0.75, se=FALSE)
plot_cro_sites_collapsed
```
